A survey of HTTP caching options on the open Semantic Web

### 2015-01-19 sanity/paper1.tex
Appendix pass
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1010 43ef1190-90fd-4dd7-a769-d0121f02b80e

The parallel spider would then launch a process per host, but each
request to one host would be delayed by 10 seconds. For each host, the
spider would go through the list of URLs found by previous steps for
that host. Since the BTC2014 recorded
the \httph{Expires} (an RFC7234 caching header), \httph{Last-Modified}
and \httph{ETag} (RFC7232 conditional request) headers where they
existed, we first examined if any of the resources were still fresh,
but none were. Wherever the last two headers existed, we added the
corresponding \httph{If-Modified-Since} and \httph{If-None-Match}
headers for a conditional initial request.

@@

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\footnote{https://metacpan.org/release/KJETILK/RDF-Generator-HTTP-0.003}
to the Comprehensive Perl Archive Network. We recorded whether the
conditional request showed that the BTC data were still fresh, and if
it was, we retrieved the current data, as we had not couple the
headers to the body in our original retrieval.

>>>>

The parallel spider would then launch a process per host, but each
request to one host would be delayed by 10 seconds. For each host, the
spider would go through the list of URLs found by previous steps for
that host. Since the BTC2014 recorded the \httph{Expires},
\httph{Last-Modified} and \httph{ETag} headers where they existed, we
first examined if any of the resources were still fresh, but none
were. Wherever the last two headers existed, we added the
corresponding \httph{If-Modified-Since} and \httph{If-None-Match}
headers for a conditional initial request.

@@

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\footnote{https://metacpan.org/release/KJETILK/RDF-Generator-HTTP-0.003}
to the Comprehensive Perl Archive Network. We recorded whether the
conditional request showed that the BTC data were still fresh, and if
it was, we retrieved the current data, as we had not coupled the
headers to the body in our original retrieval.
